---
title: "My Kids' Grades Shiny App"
author: "James C. Birk"
date: "February 16, 2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny App Project

For the Developing Data Products final project, I created a Shiny App that displays my childrens' grades.

All you need to do is put the grades into a csv.
 Here's the code I used:

```{r echo=TRUE}
library(shiny)
Grades <- read.csv("C:/Users/James/Documents/R/BirkGrades.csv")
colnames(Grades)<-(c("Subject","Grade","Senior","Junior","7th Grade","6th Grade"))
```
That got the grades ready for display.

Here's the original table
```{r echo=FALSE}
Grades
```


## Then I created a Shiny App

```{r ShinyGrades, echo = TRUE}
fluidPage(
  # Application title
  titlePanel("My Kids' Grades"),
  checkboxGroupInput("variable", "By Category:",
                     c("Overall" = "Grade",
                       "Andy Results" = "Senior",
                       "Vicki Results" = "Junior",
                       "Matthew Results" = "7th Grade",
                       "Steven Results" ="6th Grade")),
  tableOutput("data")
)
```
It's Easy to Use!

-Make a selection

-Compare any or all of the kids' grades to the average

-Check out their total averages in the bottom row


## What does the App Do and how does it work?
The app uses radio button inputs to display columns of data from a .csv file.  It is very easy to use. 
Here is the code from the server.R file
```{r server, echo=TRUE}
library(shiny)

function(input, output, session) {
  output$data <- renderTable({
    Grades[, c("Subject", input$variable), drop = FALSE]
  }, rownames = TRUE)
}

```









## How do I get this Shiny App?





My files for this app can be found on github under the username JamesRedLeg and the Developing Data Products Repo. 